### 2014-04-11 brains-results.tex
Work on figure captions

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution.png}
    \caption{XXXX}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{XXXX}
    \label{fig:feature-susceptibilities}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{XXXX}
    \label{fig:feature-variations}
\end{figure*}

>>>>

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution.png}
    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 39).
    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
    After a period of time, each feature becomes concentrated in a specific range of its own.}
    \label{fig:timebags-evolution}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} average susceptibility to substitution \emph{v.} average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    Each feature exhibits a specific and significant pattern favouring either high- or low-valued words for substitution.}
    \label{fig:feature-susceptibilities}
\end{figure*}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{\textbf{Feature variation upon substitution:} average feature of the appearing word minus $\mathcal{H}_0$ \emph{v.} average feature of the disappearing word in a substitution, with 95\% asymptotic confidence intervals.
    The overall position of the curve with respect to $y = 0$ indicates the direction of the cognitive bias.
    The fact that all the curves have positive slopes shows the influence of the disappearing word on the appearing word (indeed, the contraposition is that selection of the appearing word independently from the disappearing word would produce horizontal curves).
    Finally, the fact that all the curves also have slopes smaller than 1 means that the substitution operation is contractile on average: each feature will converge towards its own specific asymptotic range, which is consistent with the evolution observed in Figure~\ref{fig:timebags-evolution}.}
    \label{fig:feature-variations}
\end{figure*}
